House price

### 2023-12-01 output/paper/paper.qmd
Update model and figures

# Data

@@

@@

>>>>

Since the population in China has grown a lot in recent years.

# Data
## Data description

```{r}
#| echo: false
#| message: false
#| warning: false

#### Workspace setup ####
library(tidyverse)
library(knitr)
library(here)
library(latex2exp)
library(randomForest)
library(corrplot)
library(Metrics)
library(modelsummary)

#### Read in the cleaned data ####
data <- read_csv(here("output/data/cleaned_data.csv"), 
                 show_col_types = FALSE)

```

```{r}
#| label: tbl-data
#| tbl-cap: Description for variables
#| echo: false
#| message: false
#| warning: false

var <- c("Total_Price", "Unit_Price", "District", "Area", "Furnished", "Bedroom", "Living_Room", "Total_Floors", "Detailed_Floor", "Facing_South")
type <- c("Continuous", "Continuous", "Character", "Continuous", "Character", "Discrete", "Discrete", "Discrete", "Discrete", "Dummy")
def <- c("Total house price in yuan", "Unit house price in yuan/$m^2$", "District where the house is located", "Floor area of the house in $m^2$ ", "Decoration status of the house", "Number of bedrooms", "Number of living/dining rooms", "Total floors of the building", "Floor level of the house", "Whether the house is facing south")
kable(data.frame(var, type, def), col.names = c("Variable", "Type", "Definition"))
```

## Data visualiztion
```{r}
#| label: tbl-price
#| tbl-cap: Descriptive statistics about house price in each districts
#| echo: false
#| message: false
#| warning: false

data |> group_by(District) |>
  summarise(avg_total = round(mean(Total_Price)), 
            avg_unit = round(mean(Unit_Price)),
            avg_area = round(mean(Area))) |>
  kable(col.names = c("District", "Average total price",
                      "Average unit price", "Average floor area"))
```

```{r}
#| label: fig-con
#| echo: false
#| message: false
#| warning: false

df_con <- data |> select(Total_Price, Unit_Price, Area)
df_con <- gather(df_con)

df_con |> ggplot(aes(x = value)) +
  geom_histogram(fill = "#A8D8B9") +
  facet_wrap(~key, scales = "free") +
  theme_minimal()

```
```{r}
#| label: fig-dis
#| echo: false
#| message: false
#| warning: false

df_dis <- data |> select(Bedroom, Living_Room, Total_Floors, Detailed_Floor)
df_dis <- gather(df_dis)

df_dis |> ggplot(aes(x = value)) +
  geom_bar(fill = "#A8D8B9") +
  facet_wrap(~key, scales = "free") +
  theme_minimal() 
```
```{r}
#| label: fig-char
#| echo: false
#| message: false
#| warning: false
#| layout-ncol: 2

data |> group_by(District, Facing_South) |>
  summarise(n = n()) |>
  ggplot(aes(x = District, y = n, fill = factor(Facing_South))) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_fill_manual(values = c("#A8D8B9", "#FFD966"))

data |> group_by(District, Furnished) |>
  summarise(n = n()) |>
  ggplot(aes(x = District, y = n, fill = factor(Furnished))) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_fill_manual(values = c("#7FCCE5", "#FF9A8B", "#A8D8B9", "#FFD966"))
```

```{r}
#| label: fig-area
#| echo: false
#| message: false
#| warning: false

data |>
  ggplot(aes(x=Area, y=Total_Price)) +
  geom_point(alpha = 0.3, size = 0.8, color = "lightgoldenrod") +
  geom_point(data = transform(data, District = "All in Nanjing"), 
             alpha = 0.5, size = 0.8, color = "lightgoldenrod") +
  geom_smooth(data = transform(data, District = "All in Nanjing"),
              aes(color = "Non-linear"), se=F, size=0.5) +
  geom_smooth(data = transform(data, District = "All in Nanjing"),
              method = "lm", aes(color = "Linear"), se=F, size=0.5) +
  facet_wrap(~District, scales = "free") +
  theme_minimal() +
  geom_smooth(aes(color = "Non-linear"), se=F, size=0.5) +
  geom_smooth(method = "lm", aes(color = "Linear"), se=F, size=0.5) +
  labs(x = TeX(r"(Area in $m^2$)"), y = "Total Price") +
  scale_colour_manual(name = "Line", values = c("steelblue3", "indianred3")) +
  theme(legend.position = "bottom", axis.text = element_text(size = 6),
        strip.text.x = element_text(size = 8))
```
```{r}
#| label: fig-price
#| echo: false
#| message: false
#| warning: false

data |>
  ggplot(aes(x=Unit_Price, y=Total_Price)) +
  geom_point(alpha = 0.3, size = 0.8, color = "lightgoldenrod") +
  geom_point(data = transform(data, District = "All in Nanjing"), 
             alpha = 0.3, size = 0.8, color = "lightgoldenrod") +
  geom_smooth(data = transform(data, District = "All in Nanjing"),
              aes(color = "Non-linear"), se=F, size=0.5) +
  geom_smooth(data = transform(data, District = "All in Nanjing"),
              method = "lm", aes(color = "Linear"), se=F, size=0.5) +
  facet_wrap(~District, scales = "free") +
  theme_minimal() +
  geom_smooth(aes(color = "Non-linear"), se=F, size=0.5) +
  geom_smooth(method = "lm", aes(color = "Linear"), se=F, size=0.5) +
  labs(x = TeX(r"(Area in $m^2$)"), y = "Total Price") +
  scale_colour_manual(name = "Line", values = c("steelblue3", "indianred3")) +
  theme(legend.position = "bottom", axis.text = element_text(size = 6),
        strip.text.x = element_text(size = 8))
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
#### Split training and testing sets ####
set.seed(777)
trainid <- sample(nrow(data), 0.8*nrow(data))
train <- data[trainid,]
test <- data[-trainid,]
```

```{r}
#| label: model
#| echo: false
#| warning: false
#| message: false

model_mlg <- lm(Total_Price ~., data = train)
#summary(model_mlg)

model_rf <- randomForest(Total_Price ~., data=train, importance = TRUE)

#varImpPlot(model_rf)
```

@@

```{r}
#| label: rf
#| echo: false
#| warning: false
#| message: false

predict_rf_test <- predict(model_rf, newdata = test)
mae_rf_test <- round(mae(test$Total_Price, predict_rf_test),1)
rmse_rf_test <- round(rmse(test$Total_Price, predict_rf_test),1)

predict_rf_train <- predict(model_rf, newdata = train)
mae_rf_train <- round(mae(train$Total_Price, predict_rf_train),1)
rmse_rf_train <- round(rmse(train$Total_Price, predict_rf_train),1)

```

```{r}
#| label: mlg
#| echo: false
#| warning: false
#| message: false

predict_mlg_test <- predict(model_mlg, newdata = test)
mae_mlg_test <- round(mae(test$Total_Price, predict_mlg_test),1)
rmse_mlg_test <- round(rmse(test$Total_Price, predict_mlg_test),1)

predict_mlg_train <- predict(model_mlg, newdata = train)
mae_mlg_train <- round(mae(train$Total_Price, predict_mlg_train),1)
rmse_mlg_train <- round(rmse(train$Total_Price, predict_mlg_train),1)

```

```{r}
#| label: tbl-metrics
#| tbl-cap: Summary of different metrics for test and train data for two models
#| echo: false
#| message: false
#| warning: false

MAE <- c(mae_mlg_train, mae_mlg_test, mae_rf_train, mae_rf_test)
RMSE <- c(rmse_mlg_train, rmse_mlg_test, rmse_rf_train, rmse_rf_test)
Model <- c("MlG train", "MLG test", "RF train", "RF test")
metrics <- data.frame(Model, MAE, RMSE)
kable(metrics)

```

```{r}
#| label: tbl-model
#| tbl-cap: Summary of the multiple linear regression model
#| echo: false
#| message: false
#| warning: false
modelsummary(model_mlg)

```

```{r}
#| label: fig-model
#| echo: false
#| message: false
#| warning: false
#| 
ImpData <- as.data.frame(importance(model_rf))
ImpData$Var.Names <- row.names(ImpData)

ggplot(ImpData, aes(x=Var.Names, y=`%IncMSE`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`%IncMSE`), color="skyblue") +
  geom_point(aes(size = IncNodePurity), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )

```

```{r}
#| label: fig-cor
#| echo: false
#| warning: false
#| message: false

cor_matrix <- cor(data.frame(data$Total_Price, data$Unit_Price, data$Area, data$Bedroom, data$Living_Room, data$Total_Floors, data$Detailed_Floor, data$Facing_South))

corrplot(cor_matrix)
```

RUNNING TIME
